humanCdGF_predict_cfu

### 2016-10-19 code/CdGF_AUCRF.Rmd
remove code that remove cage/inocula otus

Predict_df <- merge(meta_file[meta_file$day %in% 0, 
                              c('human_source', 'mouse_id', 'cage_id', 'Euth_Early')],
                    rel_abund_stool, by.x = 'mouse_id', by.y = 'row.names')
Predict_cage_df <- select(Predict_df, -human_source, -mouse_id, -Euth_Early)
Predict_source_df <- select(Predict_df, -cage_id, -mouse_id, -Euth_Early)
Predict_cage_df$cage_id <- factor(Predict_cage_df$cage_id)
Predict_source_df$human_source <- factor(Predict_source_df$human_source)

# identify OTUs that predict cage/inocula
set.seed(seed)
rf_cage <- randomForest(cage_id ~ ., data=Predict_cage_df, importance=TRUE, ntree=n_trees)
set.seed(seed)
rf_source <- randomForest(human_source ~ ., data=Predict_source_df, importance=TRUE, ntree=n_trees)
features_source <- head(sort(rf_source$importance[ , 'MeanDecreaseAccuracy'], decreasing = T), n_features)
features_cage <- head(sort(rf_cage$importance[ , 'MeanDecreaseAccuracy'], decreasing = T), n_features)
features_all <- unique(c(names(features_cage), names(features_source)))

# remove cage/inocula OTUs from prediction dataframes
Predict_early_euth_df <- select(Predict_df, -cage_id, -mouse_id, -human_source, -one_of(features_all))

>>>>

Predict_df <- merge(meta_file[meta_file$day %in% 0, 
                              c('human_source', 'mouse_id', 'cage_id', 'Euth_Early')],
                    rel_abund_stool, by.x = 'mouse_id', by.y = 'row.names')

# remove cage/inocula OTUs from prediction dataframes
Predict_early_euth_df <- select(Predict_df, -cage_id, -mouse_id, -human_source)

### 2016-10-19 code/HumanCdGF_predict_cfu.Rmd
remove code that remove cage/inocula otus

Cage_dep_df <- meta_data %>% 
  filter(day == 0) %>% 
  select(human_source, sample_id, cage_id) %>% 
  left_join(rel_abund_shared_01)
Predict_cage_df <- select(Cage_dep_df, -human_source, -sample_id)
Predict_source_df <- select(Cage_dep_df, -cage_id, -sample_id)
Predict_cage_df$cage_id <- factor(Predict_cage_df$cage_id)
Predict_source_df$human_source <- factor(Predict_source_df$human_source)

# identify OTUs that predict cage/inocula
set.seed(seed)
rf_cage <- randomForest(cage_id ~ ., data=Predict_cage_df, importance=TRUE, ntree=n_trees)
set.seed(seed)
rf_source <- randomForest(human_source ~ ., data=Predict_source_df, importance=TRUE, ntree=n_trees)
features_source <- head(sort(rf_source$importance[ , 'MeanDecreaseAccuracy'], decreasing = T), 65)
features_cage <- head(sort(rf_cage$importance[ , 'MeanDecreaseAccuracy'], decreasing = T), 65)
cage_source_features <- unique(c(names(features_cage), names(features_source)))

colonized_cfu <- meta_data %>% 
  filter(day %in% c(4:10), !cage_id == 'NP1', 
         Early_Euth == FALSE, cdiff_strain == 431) %>% 
  select(mouse_id, cage_id, log_cfu) %>% 
  group_by(mouse_id, cage_id) %>% 
  summarise(log_cfu_med = median(log_cfu)) %>% 
  ungroup()
sample_list_d0 <- shared_list_days %>% 
    filter(day == 0) %>% 
    select(-day)
community_d0.df <- rel_abund_shared_01 %>% 
    right_join(sample_list_d0) %>% 
    select(-sample_id)
cfu_shared_colonized.df <- colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(-mouse_id, -cage_id, -one_of(cage_source_features)) %>% 
    filter(!is.na(log_cfu_med))

@@

shared_col_rate.df <- col_rate %>% 
    right_join(community_d0.df) %>% 
    select(-one_of(cage_source_features))
shared_colonized.df <- select(shared_col_rate.df, -mouse_id, -cage_id)

>>>>

colonized_cfu <- meta_data %>% 
  filter(day %in% c(4:10), !cage_id == 'NP1', 
         Early_Euth == FALSE, cdiff_strain == 431) %>% 
  select(mouse_id, cage_id, log_cfu) %>% 
  group_by(mouse_id, cage_id) %>% 
  summarise(log_cfu_med = median(log_cfu)) %>% 
  ungroup()
sample_list_d0 <- shared_list_days %>% 
    filter(day == 0) %>% 
    select(-day)
community_d0.df <- rel_abund_shared_01 %>% 
    right_join(sample_list_d0) %>% 
    select(-sample_id)
cfu_shared_colonized.df <- colonized_cfu %>% 
    right_join(community_d0.df) %>% 
    select(-mouse_id, -cage_id) %>% 
    filter(!is.na(log_cfu_med))

@@

shared_col_rate.df <- col_rate %>% 
    right_join(community_d0.df)
shared_colonized.df <- select(shared_col_rate.df, -mouse_id, -cage_id)
